Poincar\'e--Friedrichs constants over domains with shellable triangulations

### 2024-06-28 main.tex
rewriting

We write $C^{\infty}\Alt^{k}(\Omega)$ for the space of smooth differential $k$-forms over $\Omega \subseteq \bbR^{n}$,
which is the vector space of smooth mappings from $\Omega$ into $\Alt^{k}(\bbR^{n})$.
The exterior derivative \( \cartan \) is an operator that takes a \( k \)-form \( \omega \in C^{\infty}\Alt^{k}(\Omega) \) 
to a \((k+1)\)-form \( \cartan\omega \in C^{\infty}\Alt^{k+1}(\Omega) \). 
Every \( k \)-form \( \omega \in C^{\infty}\Alt^{k}(\Omega) \) can be written 
\[
    \omega = 
    \sum_{ \sigma \in \Sigma(k,n) } 
    \omega_{\sigma} \, 
    \cartanx^{\sigma(1)} \wedge \cartanx^{\sigma(2)} \wedge \cdots \wedge \cartanx^{\sigma(k)},
\]
where \( \omega_{\sigma} : \Omega \rightarrow \bbR \) are smooth functions.
The exterior derivative \( \cartan\omega \) is defined by
\[
    \cartan\omega = 
    \sum_{ \sigma \in \Sigma(k,n) } 
    \sum_{j=1}^{n} 
    \frac{\partial \omega_{\sigma}}{\partial x^j} 
    \, \cartanx^j \wedge 
    \cartanx^{\sigma(1)} \wedge \cartanx^{\sigma(2)} \wedge \cdots \wedge \cartanx^{\sigma(k)}.
\]
The exterior derivative is linear and nilpotent, which means 
\( \cartan(\cartan\omega) = 0 \) for any \( \omega \in C^{\infty}\Alt^{k}(\Omega) \).
Moreover, it satisfies the Leibniz rule:
\[ 
    \cartan(\omega \wedge \eta) 
    = 
    \cartan\omega \wedge \eta + (-1)^{k} \omega \wedge \cartan\eta, 
    \qquad \omega \in C^{\infty}\Alt^{k}(\Omega), 
    \qquad \eta \in C^{\infty}\Alt^{l}(\Omega).
\]
Let us now turn our attention to Sobolev spaces of differential forms. 
Since $\Alt^{k}(\Omega)$ is a normed space, we can consider the pointwise norms of differential $k$-forms. 
% First, we notice that the % TODO: introduce a norm 
We let $L^{p}\Alt^{k}(\Omega)$ be the space of differential $k$-forms over $\Omega$ with locally integrable coefficients 
such that its pointwise norm is $p$-integrable. 
The exterior derivative is defined in the sense of distributions and we introduce 
\[
    W^p\Alt^{k}(\Omega) = \{ u \in L^{p}\Alt^{k}(\Omega) \suchthat \cartan v \in L^{p}\Alt^{k+1}(\Omega) \}
\]
We are interested in transformations of these Sobolev tensor fields from one domain onto the other. 
Suppose that $\Omega,\Omega' \subset \bbR^{n}$ are open sets and suppose that $\phi: \Omega \to \Omega'$ is a bi-Lipschitz mapping.
The pullback of $u \in W^p\Alt^{k}(\Omega')$ along $\phi$ is the differential form 
\[ 
    \phi^{\ast}u_{|x}( v_{1}, v_{2}, \ldots, v_{k} ) 
    = 
    u_{|\phi(x)}( \Jacobian\phi_{|x} \cdot v_1, \Jacobian\phi_{|x} \cdot v_2, \ldots, \Jacobian\phi_{|x} \cdot v_k ) 
\]
for any $v_1, v_2, \dots, v_k \in \bbR^{n}$ and any $x \in \Omega$. One can show that $\phi^{\ast}u \in W^p\Alt^{k}(\Omega)$.

@@

We begin with the Poincar\'e operator. 
Suppose that $u \in C^{\infty}(\Omega,\Alt^{\ell})$ with $1 \leq \ell \leq n$.
We pointwise estimate $\Poinc_{\ell} u(x)$ for any $x \in \Omega$ by the result of a convolution of a locally integrable function with $u$:
\begin{align*}
    \left| \Poinc_{\ell} u(x) \right|
    &=
    \left| 
        \int_{\Omega} G_{n-\ell+1}(x,y) \,(x-y)\lrcorner u(y)\,dy
    \right| 
%     \\&\leq 
%     \int_{\Omega} |\Omega|^{-1} \sum_{k=0}^{(n-\ell+1)-1}\tbinom{(n-\ell+1)-1}{k} \frac{ D^{n-k} }{n-k} |x-y|^{k+1-n} |u(y)| \,dy
    \\&\leq 
    \int_{\Omega} |\Omega|^{-1} \sum_{k=0}^{ n-\ell }\tbinom{ n-\ell }{k} \frac{ D^{n-k} }{n-k} |x-y|^{k+1-n} \chi_{B_D(0)}(x-y) |u(y)| \,dy
    .
\end{align*}
We recall the radial integrals 
\begin{align*}
    \int_{B_D(0)} |z|^{k+1-n} dz
    =
    \vol_{n-1}(S_1) \int_0^D r^{k+1-n} r^{n-1} dr
    =
    \vol_{n-1}(S_1) \int_0^D r^{k} dr
    =
    \vol_{n-1}(S_1) \frac{D^{k+1}}{k+1}
    .
\end{align*}
We compute 
\begin{align*}
    &
    \int_{\bbR^{n}} \sum_{k=0}^{n-\ell} \tbinom{n-\ell}{k} \frac{ D^{n-k} }{n-k} \chi_{B_D(0)}(z) |z|^{k+1-n} \,dz
    \\&
    =
    \sum_{k=0}^{n-\ell} \tbinom{n-\ell}{k} \frac{ D^{n-k} }{n-k} \int_{B_D(0)} |z|^{k+1-n} \,dz
    \\&
    =
    \vol_{n-1}(S_1) \sum_{k=0}^{n-\ell} \tbinom{n-\ell}{k} \frac{ D^{n-k} }{n-k} \frac{D^{k+1}}{k+1}
    %\\&
    =
    \vol_{n-1}(S_1) D^{n+1} \underbrace{ \sum_{k=0}^{n-\ell} \frac{ \tbinom{n-\ell}{k} }{ (n-k)(k+1) } }_{ =: A_{\Poinc}(n,\ell) \leq 2^{n-\ell}}
    .
\end{align*}
Here, $A_{\Poinc}(n,\ell)$ is a numerical constant that depends only on $n$ and $\ell$ 
and which is bounded by $2^{n-\ell}$. 
In particular, the integral $\Poinc_{\ell} u(x)$ is absolutely convergent for any choice of $x \in \Omega$. 
So the convolution of $u$ is taken against an integrable function. 
Young's convolution inequality now implies: 
\begin{align*}
    \| \Poinc_{\ell} u \|_{L^{p}(\Omega)}
    &\leq 
    \vol_{n-1}(S_1) A_{\Poinc}(n,\ell) \frac{ D^{n} }{|\Omega|} 
    D
    \| u \|_{L^{p}(\Omega)}
    \leq 
    n A_{\Poinc}(n,\ell) \frac{ \vol_{n}(B_D(0)) }{|\Omega|} 
    D
    \| u \|_{L^{p}(\Omega)}
    .
\end{align*}
We have assumed so far that $u \in C^{\infty}(\Omega,\Alt^{\ell})$. 
Since that space is dense in the Lebesgue spaces, a density argument establishes the following: 
for any $1 \leq p \leq \infty$ we have a bounded linear operator 
\[
    \Poinc_{\ell} : L^{p}(\Omega,\Alt^{\ell}) \rightarrow L^{p}(\bbR^n,\Alt^{\ell-1}).
\]
Its operator norm is bounded by $n A_{\Poinc}(n,\ell) |\Omega|^{-1} \vol_{n}(B_D(0)) D$.

We analyze the Bogovski\u{\i} potential operator with similar means. 
Suppose that $u \in C^{\infty}_{c}(\Omega,\Alt^{\ell})$ and that $x \in \bbR^{n}$.
First, if $x \notin \Omega$, then the convexity of $\Omega$ implies that $y + t( x - y ) \notin \Omega$ for all $t > 1$. Hence $G(x,y) = 0$ and therefore $\Bogov_{\ell} u(x) = 0$ in that case.
Consider now the case $x \in \overline\Omega$. 
We estimate $\Bogov_{\ell} u(x)$ pointwise by 
\begin{align*}
    \left| \Bogov_{\ell} u(x) \right|
    &=
    \left| 
        \int_{\Omega} G_{\ell}(x,y) \,(x-y)\lrcorner u(y)\,dy
    \right| 
    \\&\leq 
    \int_{\Omega} |\Omega|^{-1} \sum_{k=0}^{\ell-1}\tbinom{\ell-1}{k} \frac{ D^{n-k} }{n-k} |x-y|^{k+1-n} |u(y)| \,dy
    \\&\leq 
    \int_{\bbR^{n}} |\Omega|^{-1} \sum_{k=0}^{\ell-1}\tbinom{\ell-1}{k} \frac{ D^{n-k} }{n-k} \chi_{B_D(0)}(x-y) |x-y|^{k+1-n} |u(y)| \,dy
    .
\end{align*}
Using once more the radial integrals discussed above, we compute 
% We recall the radial integrals 
% \begin{align*}
%     \int_{B_D(0)} |z|^{k+1-n} dz
%     =
%     \vol_{n-1}(S_1) \int_0^D r^{k+1-n} r^{n-1} dr
%     =
%     \vol_{n-1}(S_1) \int_0^D r^{k} dr
%     =
%     \vol_{n-1}(S_1) \frac{D^{k+1}}{k+1}
%     .
% \end{align*}
% We compute 
\begin{align*}
    &
    \int_{\bbR^{n}} \sum_{k=0}^{\ell-1} \tbinom{\ell-1}{k} \frac{ D^{n-k} }{n-k} \chi_{B_D(0)}(z) |z|^{k+1-n} \,dz
    \\&
    =
    \sum_{k=0}^{\ell-1} \tbinom{\ell-1}{k} \frac{ D^{n-k} }{n-k} \int_{B_D(0)} |z|^{k+1-n} \,dz
    \\&
    =
    \vol_{n-1}(S_1) \sum_{k=0}^{\ell-1} \tbinom{\ell-1}{k} \frac{ D^{n-k} }{n-k} \frac{D^{k+1}}{k+1}
    %\\&
    =
    \vol_{n-1}(S_1) D^{n+1} \underbrace{ \sum_{k=0}^{\ell-1} \frac{ \tbinom{\ell-1}{k} }{ (n-k)(k+1) } }_{ =: A_{\Bogov}(n,\ell) \leq 2^{\ell-1}}
    .
\end{align*}
Here, $A_{\Bogov}(n,\ell)$ is a numerical constant that depends only on $n$ and $\ell$ 
and which is bounded by $2^{\ell-1}$. 
In particular, the integral $\Bogov_{\ell} u(x)$ is absolutely convergent for any choice of $x \in \bbR^{n}$. 
So the convolution of $u$ is taken against an integrable function. 
Young's convolution inequality now implies: 
\begin{align*}
    \| \Bogov_{\ell} u \|_{L^{p}(\Omega)}
    &\leq 
    \vol_{n-1}(S_1) A(n,\ell) \frac{ D^{n} }{|\Omega|} 
    D
    \| u \|_{L^{p}(\Omega)}
    \leq 
    n A_{\Bogov}(n,\ell) \frac{ \vol_{n}(B_D(0)) }{|\Omega|} 
    D
    \| u \|_{L^{p}(\Omega)}
    .
\end{align*}
We have assumed so far that $u \in C^{\infty}_{c}(\Omega,\Alt^{\ell})$. 
Since that space is dense in the Lebesgue spaces, a density argument yields: 
for any $1 \leq p \leq \infty$ we have a bounded linear operator 
\[
    \Bogov_{\ell} : L^{p}(\Omega,\Alt^{\ell}) \rightarrow L^{p}(\bbR^n,\Alt^{\ell-1}).
\]
Its operator norm is bounded by $n A_{\Bogov}(n,\ell) |\Omega|^{-1} \vol_{n}(B_D(0)) D$. 
Moreover, $\supp \Bogov_{\ell} u \subseteq \overline\Omega$,
that is, the reconstructed potential has support contained within $\overline\Omega$. 
\\

Additional properties of these operators become apparent after a change of variables. 
We write down the full definition of these operators and perform two substitutions.
For the Poincar\'e operator, we substitute $a = x + t(y-x)$ and then we substitute $s = (t-1)/t$,
leading to 
\begin{align*}
    \Poinc_{\ell} u(x) 
    &= 
    \int \int_{1}^\infty (t-1)^{\ell-1}t^{n-\ell} 
    \chi_{\Omega}\left(x+t(y-x)\right) 
    (x-y)\lrcorner u(y) \,dt\,dy 
    \\
    &=
    \int \chi_{\Omega}(a) \,(x-a)\lrcorner \int_{0}^{1} t^{\ell-1} u\left(a+t(x-a)\right)\,dt\,da\;
    .
\end{align*}
For the Bogoski\u{\i} operator, we substitute $a = y + t(x-y)$ and then we substitute $s = t/(t-1)$,
leading to 
\begin{align*}
    \Bogov_{\ell} u(x) 
    &= 
    \int \int_{1}^\infty (t-1)^{n-\ell}t^{\ell-1} 
    \chi_{\Omega}\left(y+t(x-y)\right) 
    (x-y)\lrcorner u(y) \,dt\,dy 
    \\
    &=
    - \int \chi_{\Omega}(a) \,(x-a)\lrcorner \int_{1}^\infty t^{\ell-1} u\left(a+t(x-a)\right)\,dt\,da\;
    .
\end{align*}
% We first discuss the support properties of this operator. 
% Suppose that $u \in C^{\infty}(\bbR^n,\Alt^{\ell-1})$ satisfies $\supp u \subseteq \overline\Omega$.
% Then $\Bogov_{\ell} u(x) = 0$ whenever $x \notin \overline\Omega$,
% meaning $\supp \Bogov_{\ell} u \subseteq \overline\Omega$.
% 
Given $a \in \Omega$, we introduce the potential operators 
\begin{align*}
    \Poinc_{\ell,a} u(x) 
    &:= 
    (x-a)\lrcorner \int_{0}^{1} t^{\ell-1} u\left(a+t(x-a)\right)\,dt\;
    ,
    \\
    \Bogov_{\ell,a} u(x) 
    &:= 
    - (x-a)\lrcorner \int_{1}^\infty t^{\ell-1} u\left(a+t(x-a)\right)\,dt\;
    .
\end{align*}
By definition,
\begin{align*}
    \Poinc_{\ell} u(x) 
    =
    \int_{\Omega} \Poinc_{\ell,a} u(x) \,da\;,
    \quad 
    \Bogov_{\ell} u(x) 
    =
    \int_{\Omega} \Bogov_{\ell,a} u(x) \,da\;
    .
\end{align*}
We study the interaction of these potential operator with the exterior derivative in more detail.

The following discussion is classical and establishes the exactness of several de~Rham complexes. 
We recapitulate these arguments since our variants of the regularized potential operators 
are not yet included in the published literature.

@@

\begin{lemma}
    Let $\Omega \subseteq \bbR^{n}$ be convex.
    If $1 \leq p < \infty$ and $u \in C^{\infty}\Lambda^{k}(\Omega)$ with $\cartan u = 0$,
    then there exists $u_{n} \in C^{\infty}\Lambda^{k}(\Omega)$ with $\cartan u_{n} = 0$ that converges to $u$ in $L^{p}$.
\end{lemma}
\begin{proof}
    % TODO
\end{proof}

@@

The main results of this section are summarized as follows.
These results also imply the Poincar\'--Friedrichs inequalities that we have been looking for. 
These constants are proportional to the domain diameter and are independent of the Lebesgue exponent $1 \leq p \leq \infty$,
though the dimension and the form degree enters the estimate.

\begin{theorem}
    Let $\Omega \subseteq \bbR^{n}$ be convex and let $1 \leq p < \infty$. 
    We have bounded operators 
    \begin{align*}
        \Poinc_{\ell} : L^{p}(\Omega,\Alt^{\ell}) \rightarrow \bfW^{p}_{0}(\Omega,\Alt^{\ell-1})
        ,
        \qquad 
        \Bogov_{\ell} : L^{p}(\Omega,\Alt^{\ell}) \rightarrow \bfW^{p}_{0}(\Omega,\Alt^{\ell-1})
        .
    \end{align*}
    They satisfy the operator norm bounds 
    \begin{align*}
        \| \Poinc_{\ell} u \|_{L^{p}(\Omega)}
        &\leq 
        n A_{\Poinc}(n,\ell) \frac{ \vol_{n}(B_D(0)) }{|\Omega|} 
        D
        \| u \|_{L^{p}(\Omega)}
        ,
        \\
        \| \Bogov_{\ell} u \|_{L^{p}(\Omega)}
        &\leq 
        n A_{\Bogov}(n,\ell) \frac{ \vol_{n}(B_D(0)) }{|\Omega|} 
        D
        \| u \|_{L^{p}(\Omega)}
        .
    \end{align*}
    If $u \in \bfW^{p}    (\Omega,\Alt^{\ell})$ with $\cartan u = 0$, then $\Poinc_{\ell} u \in \bfW^{p}    (\Omega,\Alt^{\ell  })$ with $u = \cartan \Poinc_{\ell} u$.
    If $u \in \bfW^{p}_{0}(\Omega,\Alt^{\ell})$ with $\cartan u = 0$, then $\Bogov_{\ell} u \in \bfW^{p}_{0}(\Omega,\Alt^{\ell-1})$ with $u = \cartan \Bogov_{\ell} u$.
\end{theorem}
\begin{proof}
    The potential operators are linear and the operator norm bounds are satisfied over the dense subspace $C^{\infty}_{c}(\Omega,\Alt^{\ell})$.

>>>>

We write $C^{\infty}\Alt^{k}(\Omega)$ for the space of smooth differential $k$-forms over $\Omega \subseteq \bbR^{n}$,
which is the vector space of smooth mappings from $\Omega$ into $\Alt^{k}(\bbR^{n})$.
The exterior derivative \( \cartan \) is an operator that takes a \( k \)-form \( \omega \in C^{\infty}\Alt^{k}(\Omega) \) 
to a \((k+1)\)-form \( \cartan\omega \in C^{\infty}\Alt^{k+1}(\Omega) \). 
Every \( k \)-form \( \omega \in C^{\infty}\Alt^{k}(\Omega) \) can be written 
\[
    \omega = 
    \sum_{ \sigma \in \Sigma(k,n) } 
    \omega_{\sigma} \, 
    \cartanx^{\sigma(1)} \wedge \cartanx^{\sigma(2)} \wedge \cdots \wedge \cartanx^{\sigma(k)},
\]
where \( \omega_{\sigma} : \Omega \rightarrow \bbR \) are smooth functions.
The exterior derivative \( \cartan\omega \) is defined by
\[
    \cartan\omega = 
    \sum_{ \sigma \in \Sigma(k,n) } 
    \sum_{j=1}^{n} 
    \frac{\partial \omega_{\sigma}}{\partial x^j} 
    \, \cartanx^j \wedge 
    \cartanx^{\sigma(1)} \wedge \cartanx^{\sigma(2)} \wedge \cdots \wedge \cartanx^{\sigma(k)}.
\]
The exterior derivative is linear and nilpotent, which means 
\( \cartan(\cartan\omega) = 0 \) for any \( \omega \in C^{\infty}\Alt^{k}(\Omega) \).
Moreover, it satisfies the Leibniz rule:
\[ 
    \cartan(\omega \wedge \eta) 
    = 
    \cartan\omega \wedge \eta + (-1)^{k} \omega \wedge \cartan\eta, 
    \qquad \omega \in C^{\infty}\Alt^{k}(\Omega), 
    \qquad \eta \in C^{\infty}\Alt^{l}(\Omega).
\]
Let us now turn our attention to Sobolev spaces of differential forms. 
Since $\Alt^{k}(\Omega)$ is a normed space, we can consider the pointwise norms of differential $k$-forms. 
% First, we notice that the % TODO: introduce a norm 
We let $L^{p}\Alt^{k}(\Omega)$ be the space of differential $k$-forms over $\Omega$ with locally integrable coefficients 
such that its pointwise norm is $p$-integrable. 
The exterior derivative is defined in the sense of distributions and we introduce 
\[
    W^p\Alt^{k}(\Omega) = \{ u \in L^{p}\Alt^{k}(\Omega) \suchthat \cartan v \in L^{p}\Alt^{k+1}(\Omega) \}
\]
We observe that $u \in L^p\Alt^{k}(\Omega)$ has weak exterior derivative $f \in L^p\Alt^{k+1}(\Omega)$
if and only if for all $v \in C^{\infty}_{c}\Lambda^{n-k-1}(\Omega)$ we have the integration by parts formula
\begin{align*}
    \int_{\Omega} \cartan v \wedge u
    &=
    (-1)^{k(n-k)+1}
    \int_{\Omega} v \wedge f 
    .
\end{align*}
We are interested in transformations of these Sobolev tensor fields from one domain onto the other. 
Suppose that $\Omega,\Omega' \subset \bbR^{n}$ are open sets and suppose that $\phi: \Omega \to \Omega'$ is a bi-Lipschitz mapping.
The pullback of $u \in W^p\Alt^{k}(\Omega')$ along $\phi$ is the differential form 
\[ 
    \phi^{\ast}u_{|x}( v_{1}, v_{2}, \ldots, v_{k} ) 
    = 
    u_{|\phi(x)}( \Jacobian\phi_{|x} \cdot v_1, \Jacobian\phi_{|x} \cdot v_2, \ldots, \Jacobian\phi_{|x} \cdot v_k ) 
\]
for any $v_1, v_2, \dots, v_k \in \bbR^{n}$ and any $x \in \Omega$. One can show that $\phi^{\ast}u \in W^p\Alt^{k}(\Omega)$.

@@

We begin with the Poincar\'e operator. 
Suppose that $u \in L^{\infty}\Alt^{\ell}(\Omega)$ with $1 \leq \ell \leq n$.
We pointwise estimate $\Poinc_{\ell} u(x)$ for any $x \in \Omega$ by the result of a convolution of a locally integrable function with $u$:
    \left| \Poinc_{\ell} u(x) \right|
    \left| 
        \int_{\Omega} G_{n-\ell+1}(x,y) \,(x-y)\lrcorner u(y)\,dy
    \right| 
%     \\&\leq 
%     \int_{\Omega} |\Omega|^{-1} \sum_{k=0}^{(n-\ell+1)-1}\tbinom{(n-\ell+1)-1}{k} \frac{ D^{n-k} }{n-k} |x-y|^{k+1-n} |u(y)| \,dy
    \\&\leq 
    \int_{\Omega} |\Omega|^{-1} \sum_{k=0}^{ n-\ell }\tbinom{ n-\ell }{k} \frac{ D^{n-k} }{n-k} |x-y|^{k+1-n} \chi_{B_D(0)}(x-y) |u(y)| \,dy
We recall the radial integrals 
    \int_{B_D(0)} |z|^{k+1-n} dz
    \vol_{n-1}(S_1) \int_0^D r^{k+1-n} r^{n-1} dr
    \vol_{n-1}(S_1) \int_0^D r^{k} dr
    \vol_{n-1}(S_1) \frac{D^{k+1}}{k+1}
We compute 
    \int_{\bbR^{n}} \sum_{k=0}^{n-\ell} \tbinom{n-\ell}{k} \frac{ D^{n-k} }{n-k} \chi_{B_D(0)}(z) |z|^{k+1-n} \,dz
    \sum_{k=0}^{n-\ell} \tbinom{n-\ell}{k} \frac{ D^{n-k} }{n-k} \int_{B_D(0)} |z|^{k+1-n} \,dz
    \vol_{n-1}(S_1) \sum_{k=0}^{n-\ell} \tbinom{n-\ell}{k} \frac{ D^{n-k} }{n-k} \frac{D^{k+1}}{k+1}
    %\\&
    \vol_{n-1}(S_1) D^{n+1} \underbrace{ \sum_{k=0}^{n-\ell} \frac{ \tbinom{n-\ell}{k} }{ (n-k)(k+1) } }_{ =: A_{\Poinc}(n,\ell) \leq 2^{n-\ell}}
Here, $A_{\Poinc}(n,\ell)$ is a numerical constant that depends only on $n$ and $\ell$ 
and which is bounded by $2^{n-\ell}$. 
In particular, the integral $\Poinc_{\ell} u(x)$ is absolutely convergent for any choice of $x \in \Omega$. 
So the convolution of $u$ is taken against an integrable function. 
Young's convolution inequality now implies: 
    \| \Poinc_{\ell} u \|_{L^{p}(\Omega)}
    &\leq 
    \vol_{n-1}(S_1) A_{\Poinc}(n,\ell) \frac{ D^{n} }{|\Omega|} 
    D
    \| u \|_{L^{p}(\Omega)}
    \leq 
    n A_{\Poinc}(n,\ell) \frac{ \vol_{n}(B_D(0)) }{|\Omega|} 
    D
    \| u \|_{L^{p}(\Omega)}
We have assumed so far that $u \in L^{\infty}\Alt^{\ell}(\Omega)$. 
Since that space is dense in the Lebesgue spaces, a density argument establishes the following: 
for any $1 \leq p \leq \infty$ we have a bounded linear operator 
\[
    \Poinc_{\ell} : L^{p}\Alt^{\ell}(\Omega) \rightarrow L^{p}(\bbR^n,\Alt^{\ell-1}).
\]
% Its operator norm is bounded by $n A_{\Poinc}(n,\ell) |\Omega|^{-1} \vol_{n}(B_D(0)) D$. 
% 
We analyze the Bogovski\u{\i} potential operator with similar means. 
Suppose that $u \in L^{\infty}\Alt^{\ell}(\bbR^{n})$ with $\supp u \subseteq \overline\Omega$ and that $x \in \bbR^{n}$.
First, if $x \notin \Omega$, then the convexity of $\Omega$ implies that $y + t( x - y ) \notin \Omega$ for all $t > 1$. Hence $G(x,y) = 0$ and therefore $\Bogov_{\ell} u(x) = 0$ in that case.
Consider now the case $x \in \overline\Omega$. 
We estimate $\Bogov_{\ell} u(x)$ pointwise by 
    \left| \Bogov_{\ell} u(x) \right|
    \left| 
        \int_{\Omega} G_{\ell}(x,y) \,(x-y)\lrcorner u(y)\,dy
    \right| 
    \\&\leq 
    \int_{\Omega} |\Omega|^{-1} \sum_{k=0}^{\ell-1}\tbinom{\ell-1}{k} \frac{ D^{n-k} }{n-k} |x-y|^{k+1-n} |u(y)| \,dy
    \\&\leq 
    \int_{\bbR^{n}} |\Omega|^{-1} \sum_{k=0}^{\ell-1}\tbinom{\ell-1}{k} \frac{ D^{n-k} }{n-k} \chi_{B_D(0)}(x-y) |x-y|^{k+1-n} |u(y)| \,dy
Using once more the radial integrals discussed above, we compute 
% We recall the radial integrals 
% \begin{align*}
%     \int_{B_D(0)} |z|^{k+1-n} dz
%     =
%     \vol_{n-1}(S_1) \int_0^D r^{k+1-n} r^{n-1} dr
%     =
%     \vol_{n-1}(S_1) \int_0^D r^{k} dr
%     =
%     \vol_{n-1}(S_1) \frac{D^{k+1}}{k+1}
%     .
% \end{align*}
% We compute 
    \int_{\bbR^{n}} \sum_{k=0}^{\ell-1} \tbinom{\ell-1}{k} \frac{ D^{n-k} }{n-k} \chi_{B_D(0)}(z) |z|^{k+1-n} \,dz
    \sum_{k=0}^{\ell-1} \tbinom{\ell-1}{k} \frac{ D^{n-k} }{n-k} \int_{B_D(0)} |z|^{k+1-n} \,dz
    \vol_{n-1}(S_1) \sum_{k=0}^{\ell-1} \tbinom{\ell-1}{k} \frac{ D^{n-k} }{n-k} \frac{D^{k+1}}{k+1}
    %\\&
    \vol_{n-1}(S_1) D^{n+1} \underbrace{ \sum_{k=0}^{\ell-1} \frac{ \tbinom{\ell-1}{k} }{ (n-k)(k+1) } }_{ =: A_{\Bogov}(n,\ell) \leq 2^{\ell-1}}
Here, $A_{\Bogov}(n,\ell)$ is a numerical constant that depends only on $n$ and $\ell$ 
and which is bounded by $2^{\ell-1}$. 
In particular, the integral $\Bogov_{\ell} u(x)$ is absolutely convergent for any choice of $x \in \bbR^{n}$. 
So the convolution of $u$ is taken against an integrable function. 
Young's convolution inequality now implies: 
    \| \Bogov_{\ell} u \|_{L^{p}(\Omega)}
    &\leq 
    \vol_{n-1}(S_1) A(n,\ell) \frac{ D^{n} }{|\Omega|} 
    D
    \| u \|_{L^{p}(\Omega)}
    \leq 
    n A_{\Bogov}(n,\ell) \frac{ \vol_{n}(B_D(0)) }{|\Omega|} 
    D
    \| u \|_{L^{p}(\Omega)}
We have assumed so far that $u$ is essentially bounded.
Since that space is dense in the Lebesgue spaces, a density argument yields: 
for any $1 \leq p \leq \infty$ we have a bounded linear operator 
\[
    \Bogov_{\ell} : L^{p}\Alt^{\ell}(\Omega) \rightarrow L^{p}(\bbR^n,\Alt^{\ell-1}).
\]
% Its operator norm is bounded by $n A_{\Bogov}(n,\ell) |\Omega|^{-1} \vol_{n}(B_D(0)) D$. 
Moreover, $\supp \Bogov_{\ell} u \subseteq \overline\Omega$,
that is, the reconstructed potential has support contained within $\overline\Omega$. 
\\

Additional properties of these operators become apparent after a change of variables. 
We write down the full definition of these operators and perform two substitutions.
For the Poincar\'e operator, we substitute $a = x + t(y-x)$ and then we substitute $s = (t-1)/t$,
leading to 
\begin{align*}
    \Poinc_{\ell} u(x) 
    &= 
    \int \int_{1}^\infty (t-1)^{\ell-1}t^{n-\ell} 
    \chi_{\Omega}\left(x+t(y-x)\right) 
    (x-y)\lrcorner u(y) \,dt\,dy 
    \\
    &=
    \int \chi_{\Omega}(a) \,(x-a)\lrcorner \int_{0}^{1} t^{\ell-1} u\left(a+t(x-a)\right)\,dt\,da\;
    .
\end{align*}
For the Bogoski\u{\i} operator, we substitute $a = y + t(x-y)$ and then we substitute $s = t/(t-1)$,
leading to 
\begin{align*}
    \Bogov_{\ell} u(x) 
    &= 
    \int \int_{1}^\infty (t-1)^{n-\ell}t^{\ell-1} 
    \chi_{\Omega}\left(y+t(x-y)\right) 
    (x-y)\lrcorner u(y) \,dt\,dy 
    \\
    &=
    - \int \chi_{\Omega}(a) \,(x-a)\lrcorner \int_{1}^\infty t^{\ell-1} u\left(a+t(x-a)\right)\,dt\,da\;
    .
\end{align*}
% We first discuss the support properties of this operator. 
% Suppose that $u \in C^{\infty}(\bbR^n,\Alt^{\ell-1})$ satisfies $\supp u \subseteq \overline\Omega$.
% Then $\Bogov_{\ell} u(x) = 0$ whenever $x \notin \overline\Omega$,
% meaning $\supp \Bogov_{\ell} u \subseteq \overline\Omega$.
% 
Given $a \in \Omega$, we introduce the potential operators 
\begin{align*}
    \Poinc_{\ell,a} u(x) 
    &:= 
    (x-a)\lrcorner \int_{0}^{1} t^{\ell-1} u\left(a+t(x-a)\right)\,dt\;
    ,
    \\
    \Bogov_{\ell,a} u(x) 
    &:= 
    - (x-a)\lrcorner \int_{1}^\infty t^{\ell-1} u\left(a+t(x-a)\right)\,dt\;
    .
\end{align*}
By definition,
\begin{align*}
    \Poinc_{\ell} u(x) 
    =
    \int_{\Omega} \Poinc_{\ell,a} u(x) \,da\;,
    \quad 
    \Bogov_{\ell} u(x) 
    =
    \int_{\Omega} \Bogov_{\ell,a} u(x) \,da\;
    .
\end{align*}
We study the interaction of these potential operator with the exterior derivative in more detail.
% 
That discussion is classical and establishes the exactness of several de~Rham complexes. 
We recapitulate these arguments since our variants of the regularized potential operators 
are not yet included in the published literature.

@@

% TODO: averaging

@@

\\

% TODO: averaging

We are in the position to establish the main results of this section.
This includes upper bounds for the Poincar\'--Friedrichs inequalities that we have been looking for. 
Said upper bounds are proportional to the domain diameter and are independent of the Lebesgue exponent $1 \leq p \leq \infty$,
though the dimension and the form degree enters the estimate.

\begin{theorem}
    Let $\Omega \subseteq \bbR^{n}$ be convex and let $1 \leq p < \infty$. 
    We have bounded operators 
    \begin{align*}
        \Poinc_{\ell} : L^{p}\Alt^{\ell}(\Omega) \rightarrow \bfW^{p}_{0}\Alt^{\ell-1}(\Omega)
        ,
        \qquad 
        \Bogov_{\ell} : L^{p}\Alt^{\ell}(\Omega) \rightarrow \bfW^{p}_{0}\Alt^{\ell-1}(\Omega)
        .
    \end{align*}
    They satisfy the operator norm bounds 
    \begin{align*}
        \| \Poinc_{\ell} u \|_{L^{p}(\Omega)}
        &\leq 
        n A_{\Poinc}(n,\ell) \frac{ \vol_{n}(B_D(0)) }{|\Omega|} 
        D
        \| u \|_{L^{p}(\Omega)}
        ,
        \\
        \| \Bogov_{\ell} u \|_{L^{p}(\Omega)}
        &\leq 
        n A_{\Bogov}(n,\ell) \frac{ \vol_{n}(B_D(0)) }{|\Omega|} 
        D
        \| u \|_{L^{p}(\Omega)}
        .
    \end{align*}
    If $u \in \bfW^{p}    \Alt^{\ell}(\Omega)$ with $\cartan u = 0$, then $\Poinc_{\ell} u \in \bfW^{p}    (\Omega,\Alt^{\ell  })$ with $u = \cartan \Poinc_{\ell} u$.
    If $u \in \bfW^{p}_{0}\Alt^{\ell}(\Omega)$ with $\cartan u = 0$, then $\Bogov_{\ell} u \in \bfW^{p}_{0}\Alt^{\ell-1}(\Omega)$ with $u = \cartan \Bogov_{\ell} u$.
\end{theorem}
\begin{proof}
    The potential operators are linear and the operator norm bounds are satisfied over the dense subspace $C^{\infty}_{c}\Alt^{\ell}(\Omega)$.

    Consider now $u \in W^{p}\Alt^{\ell}(\Omega)$ with $\cartan u = 0$. 
    We write $w := \Poinc_{\ell  } u$. 
    There exists a sequence $u_{i} \in C^{\infty}(\overline\Omega,\Alt^{\ell})$ that converges to $u$ in $W^{p}\Alt^{\ell}(\Omega)$. 
    For any test form $v \in C^{\infty}_{c}(\Omega,\Alt^{n-\ell-1})$, we verify 
    \begin{align*}
        \int_{\Omega} v \wedge u_{i} 
        &=
        \int_{\Omega} v \wedge \Poinc_{\ell+1} \cartan u_{i}
        +
        \int_{\Omega} v \wedge \cartan \Poinc_{\ell  } u_{i}
        \\&=
        \int_{\Omega} v \wedge \Poinc_{\ell+1} \cartan u_{i}
        +
        (-1)^{k(n-k)+1}
        \int_{\Omega} \cartan v \wedge \Poinc_{\ell  } u_{i}
        .
    \end{align*}
    By the continuity of bounded linear functionals, we find 
    \begin{align*}
        \int_{\Omega} v \wedge u 
        &=
        (-1)^{k(n-k)+1}
        \int_{\Omega} \cartan v \wedge \Poinc_{\ell  } u_{i}
        .
    \end{align*}
    By definition, $w \in W^{p}\Alt^{\ell-1}(\Omega)$ with $\cartan w = u$.
